
\documentclass[11pt,a4paper]{article}

\usepackage[left=0.8in,top=0.8in,right=0.8in,bottom=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro}
\usepackage{xcolor}
\usepackage{titlesec}

\definecolor{titleblue}{HTML}{00199e}

\titleformat{\section}{\Large\bfseries\color{titleblue}}{}{0em}{}

\begin{document}

{\Huge \textbf{BHOOMI JAIN}}

\vspace{0.2em}

9518270384 \\
bhoomijainbj201@gmail.com

\section*{Personal Profile}

As a software development enthusiast, I leverage my technical skills to design and develop innovative software applications. Proficient in multiple programming languages, including Java, Python, and JavaScript, I excel at writing clean and efficient code. My experience with databases, APIs, and web development has prepared me for collaborative work with cross-functional teams.



\section*{Education}

• B.Tech Computer Engineering and Data Science, J.C.Bose University, YMCA, Faridabad CGPA: 8.46
• Class 12, Vishwa Bharti Public School, Jagadhri, Haryana (2023) Percentage: 83%
• Class 10, St. Thomas School, Jagadhri, Haryana Percentage: 93%



\section*{Experience}

• Student Coordinator, Manan Technical Club
– Led technical workshops and organized student collaboration activities.
– Organized a 24-hour university-level hackathon with 700+ participants from across the country.

• Student Coordinator, Placement Training Cell – UDAAN
– Mentored 100+ students during placement training programs.
– Conducted resume reviews, mock interviews, and company interactions sessions.



\section*{Projects}

AI-Powered Digital Twin Personality Assistant
- Developed a full-stack AI application that mimics a person's texting style using exported WhatsApp chat data.
- Implemented an RAG pipeline using HuggingFace embeddings and ChromaDB for semantic memory retrieval.
- Integrated local LLMinference using Ollama with LLaMA models for contextual Hindi response generation.
- Built frontend-backend API communication and implemented prompt engineering for personalized conversational replies.

AIATS Resume Optimizer
- Built an AI-powered ATS Resume Optimizer to compare resumes with job descriptions using local LLMs.
- Implemented AI-based skill extraction, keyword matching, and ATS score calculation.
- Developed AI-assisted and manual resume optimization workflow with an interactive Streamlit interface.



\section*{Skills}

• Programming Languages: Java, Python, SQL, JavaScript
• Data Structures and Algorithms: DataStructuresandAlgorithms(400+problems), OOP, DBMS, ComputerNetworks, OperatingSystems
• AI/ML: MachineLearning, DeepLearning, GenerativeAI, Retrieval-AugmentedGeneration (RAG), LangChain, ChromaDB, VectorDatabases, HuggingFaceEmbeddings, SemanticSearch, Prompt Engineering, ConversationalAI
• Web Development: HTML, CSS, JavaScript, React, Flask, Streamlit, RESTAPIs
• Tools Platforms: Git, GitHub, VSCode



\section*{Achievements}

• Completed Data Science Course from PWSkills. Certificate Link
• Secured 3rd position in a coding competition organized by IEEE YMCA.
• Conducted and hosted a beginner-friendly session on Machine Learning.


\end{document}
